Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich CSI Compression for Massive MIMO: Model-Based or Data-Driven?

@@

>>>>

\cite{CSICompression2024} systematically analyzes CSI feedback overhead challenges in massive MIMO, demonstrating that uncompressed feedback can reach 2 Mb/s per antenna. The study provides a comprehensive comparison between traditional model-driven compression and emerging data-driven approaches, noting that while machine learning methods achieve better accuracy, they incur higher computational costs. The authors evaluate deployment readiness for 5G-Advanced systems, highlighting critical trade-offs between efficiency and flexibility in practical implementations.

@@

	\bibitem{CSICompression2024}
	A. Author et al., 
	"Title of the Paper in Sentence Case," 
	\textit{IEEE Journal Name}, 
	vol. XX, no. X, 
	pp. XXX--XXX, 
	Month. Year, 
	doi: XXXXX.XXXXXX.
